---
title: "Report"
author: "Samuel Pereira"
date: "26/11/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

In this report I'll make a few points about the data on morders in US territory, I hope this little project of mine can server as a start for your own data analysis and repors.

Using this libraries:  
1. ggplot2  
2. tidyverse  

```{r libraries,message=FALSE,echo=FALSE}
library(ggplot2)
library(tidyverse)
```

And the data wrangled using the handler script

```{r data}
load("rda/murders.rda")
```


## Overview

```{r summary, echo=FALSE}
summary(murders$rate)
```
This the average death rate of the USA looks a little high if compared to european countries.   However is it fair to judge USA considering such vast territory and diverse regions? 


## deaths across regions

Let's see how the murder rates are within the country:

```{r pressure, echo=FALSE}
murders %>% ggplot(aes(region,rate))+
  ylab("Deaths per 100,000")+
  xlab("Us Regions")+
  geom_boxplot()
```


